\section{Introduction}
Recent years witnessed the rapid spreading of cellular networks and pervasive mobile devices (MDs). The telecommunication (Telco) data, as trace of MDs in cellular networks, has many important applications for Telco operators, e.g., city-scale Telco localization \cite{DBLP:conf/cikm/ZhuLYZZGDRZ16}, churn prediction of subscribers \cite{DBLP:conf/sigmod/HuangZYDLND0Z15} and user experience assessment \cite{DBLP:journals/tist/LuoZYDY16}. In particular, as an important complementary technique of GPS, Telco localization is aimed at recovering mobility patterns of MDs at fine grained level (e.g., 20 meters). Unlike the call detail records (CDRs), Telco localization techniques mainly focus on measurement records (MRs), which measures radio signal strengths (RSSIs) between MD and its connected cells in Telco networks. In the past years, a plenty of Telco localization methods have been proposed to improve the performance under challenging city environment \cite{DBLP:conf/icc/IbrahimY11, DBLP:conf/icc/HaraAYDZ11,DBLP:journals/tvt/IbrahimY12,DBLP:conf/infocom/RayDM16,DBLP:conf/infocom/MargoliesBBDJUV17}.

However, these localization models are suffering from missing signal strength (RSSI) values. Zhu \cite{DBLP:conf/cikm/ZhuLYZZGDRZ16} found that nearly 50\% of real world MR records have RSSI with only 1 or 2 cells. Ray \cite{DBLP:conf/infocom/RayDM16} proposed a localization model based on that RSSI values from neighboring cells are all missing. The missing data problem significantly deteriorates the performance of Telco localization. There are two main reasons of missing values in MR records. One is that the mobile phones do not provide API to access neighboring cells. The other is that the RSSI is lost, due to communication failure or data corruption. Consequently, it is desired to develop a methodology with high completion performance to estimate the missing data.

%State-of-the-art data completion algorithms can be classified into two categories: statistical based methods and machine learning based methods. The statistical methods include mean imputation and regression models \cite{DBLP:journals/technometrics/Lazar03a}. The machine learning based methods build a predictive model to learn the internal mappings of data. These methods include algorithms based on K-nearest neighbor \cite{DBLP:journals/bioinformatics/TroyanskayaCSBHTBA01}, matrix completion \cite{DBLP:journals/jmlr/MazumderHT10}, Expectation Maximization \cite{DBLP:journals/nca/Garcia-LaencinaSF10} and deep neural networks such as denoising autoencoder (DAE) \cite{DBLP:conf/pakdd/GondaraW18}. However, the current machine learning based models have several drawbacks. For instance, 

State-of-the-art data completion algorithms can be classified into two categories: discriminative methods and generative methods. The discriminative models maximize the conditional probability of missing components given observed components. These methods include KNN \cite{DBLP:journals/bioinformatics/TroyanskayaCSBHTBA01}, MICE\cite{buuren2010mice} and matrix completion \cite{DBLP:journals/jmlr/MazumderHT10}. The generative methods maximize the joint probability of both observed and missing components, such as algorithms based on Expectation Maximization \cite{DBLP:journals/nca/Garcia-LaencinaSF10} and deep learning (e.g., denoising autoencoder (DAE)) \cite{DBLP:conf/icml/VincentLBM08,DBLP:conf/pakdd/GondaraW18}. However, there are two main challenges to directly apply existing data completion methods into our scenario. 1) \emph{Complex interactions of MR data}: Due to complicated Telco operation design \cite{DBLP:conf/infocom/MargoliesBBDJUV17}, the internal relationship of MR data is sophisticated and nonlinear. 2) \emph{Noisy signal strength}: The challenging RF propagation phenomena (e.g., multipath and non-line-of-sight) causes noise signal strength values. Noise caused by such fluctuation can hurt the inference of missing RSSI. Existing methods with shadow capability can not capture the distribution of MR data well. Besides, by retrieving locations from location-based services, the position labels is available in training data. However, such labels are not accessible in the testing phase. It is non-trivial to incorporate the position labels of training data into missing data completion.

%Besides, there is a major difference in our problem. The missing MR data to complete is collected without location labels (e.g., GPS coordinates) due to GPS issues \cite{DBLP:conf/mdm/ZhangRYZY17}. However, by retrieving locations from location-based services, it is available in historical collected MR data \cite{DBLP:journals/imwut/HuangLWCXZ17}. How to exploit these labels to help the generation of missing RSSI remains challenging.

With recent breakthroughs in deep learning, Generative Adversarial Nets (GANs), as a powerful technique for generative modelling, has shown impressive results in realistic data generation \cite{DBLP:conf/nips/GoodfellowPMXWOCB14,DBLP:conf/cvpr/LedigTHCCAATTWS17}. The GANs plays a game between two networks: a generator that produces completed MR data given MR missing data and a discriminator that produces probability distribution between the completed and real data \cite{DBLP:conf/nips/GoodfellowPMXWOCB14}. Compared with traditional machine learning models, the competing process between two networks are better at learning sophisticated internal correlation of data.

To this end, we propose TelcoGAN that built upon GANs to address the MR missing data problem. TelcoGAN takes advantage of available GPS location labels in training data set (e.g., retrieving location corrdinates from location-based services \cite{DBLP:journals/imwut/HuangLWCXZ17}), to stabilize the training process and lead to better completion performance. Our research makes two main contributions:

\begin{itemize}
  \item We propose TelcoGAN which cooperates a \emph{serving-centric space} and a \emph{localizer network} to produce high quality complete MR data. The serving-centric space component helps to learn the internal correlation of MR. The localizer network utilizes available GPS location labels to guide the adversarial process towards better results. In addition, we adopt a hybrid loss trick which combines mean squared loss and adversarial loss to further improve the performance.
  \item Evaluations on two real-world MR data sets show that our model achieves better performance than state-of-arts and the model trained on a spatial domain can improve the performance of another one.
\end{itemize}

The rest of this paper is organized as follows. Section II gives preliminary background and some related works. In Section III, we describe the technical design of TelcoGAN in detail. After that, we conduct extensive experiments in Section IV and review some related work in Section V. Finally, we conclude in Section VI.

Table  summarizes the main symbols and associated meanings used in this paper. 